## Libraries:
```R
library(tidyverse)
library(jsonlite)
library(stringr)
library(reshape2)
```

## Custome functions:
```R
# Function to read and process a JSON file
process_json <- function(file_path) {
  summary_data <- fromJSON(file_path)
  
  if (str_detect(file_path, "penta")) {
    chain_pair_iptm <- summary_data$chain_pair_iptm[1:5, 1:5] %>% as.data.frame() %>% setNames(c(1:5))
  } else if (str_detect(file_path, "hexa")) {
    chain_pair_iptm <- summary_data$chain_pair_iptm[1:6, 1:6] %>% as.data.frame() %>% setNames(c(1:6))
  } else {
    chain_pair_iptm <- NULL
  }
  
  list(summary = summary_data, chain_pair_iptm = chain_pair_iptm)
}

# Function to process all JSON files in a directory
process_directory <- function(directory) {
  file_list <- list.files(directory, pattern = "_summary_confidences_0.json", full.names = TRUE, recursive = TRUE)
  data_list <- list()
  
  for (file_path in file_list) {
    file_name <- tools::file_path_sans_ext(basename(file_path)) # Remove extension for cleaner name
    processed_data <- process_json(file_path)
    
    if (!is.null(processed_data$chain_pair_iptm)) {
      data_list[[file_name]] <- processed_data
    }
  }
  
  return(data_list)
}
```




# Unzip the AF3 outputs and import the top ranking model confidence scores and stats here for each batch:
```R
### AF Benchmarks (AF2 vs AF3 vs AF3 w/lipids):
AF_benchmark_directory <- "/path/to/NRC2_benchmarks/"

AF_benchmark_data <- process_directory(NRC2_benchmark_directory)


### NRC2 benchmars:
## put all the NRC2 oligomer variants in the same folder /NRC2_benchmars
NRC2_benchmark_directory <- "/path/to/NRC2_benchmarks/"

NRC2_benchmark_data <- process_directory(NRC2_benchmark_directory)



### known cryo-EM model benchmarks:
benchmark_directory <- "/path/to/Benchmarks/"

benchmark_data <- process_directory(benchmark_directory)


### CC-NLRs
CC_directory <- "/path/to/CC/"

CC_data <- process_directory(CC_directory)


### CCG10-NLRs:
CCG10_directory <- "/path/to/CCG10/"

CCG10_data <- process_directory(CCG10_directory)


### CCR-NLRs:
CCR_directory <- "/path/to/CCR/"

CCR_data <- process_directory(CCR_directory)


### NRCs:
NRC_directory <- "/path/to/NRCs/"

NRC_data <- process_directory(NRC_directory)
```



# Plot the chian pair ipTMs:
```{r}
# Function to plot heatmap and save it
plot_heatmap <- function(df, sublist_name) {
  
 df$row <- as.factor(1:nrow(df))
  
  # Mirror the dataframe along the y-axis (row axis)
  df_mirrored <- df[, rev(colnames(df))]
  
  # Melt the dataframe for ggplot
  df_melt <- melt(df_mirrored, id.vars = "row")
  
  # Calculate the number of rows and columns
  num_rows <- nrow(df)
  num_cols <- ncol(df) - 1  # Subtracting 1 to account for the 'row' column
  
  # Create the plot
  p <- ggplot(df_melt, aes(x = variable, y = row, fill = value)) +
    geom_tile(color = "white") +
    geom_text(aes(label = sprintf("%.2f", value)), color = "black", size= 7) +
    scale_fill_gradient2(low = "#CC3333", mid = "#FEFEFA", high = "#1C39BB", midpoint = 0.5, limit = c(0, 1)) +
    theme_void() +
    theme(legend.position = "none")
  
  # Save the plot with the sublist name
  ggsave(filename = paste0(sublist_name, '.png'), plot = p, width = num_cols, height = num_rows)
}
```


## AF benchmark:
```{r}
setwd("/path/to/figures/AF_benchmark")

for (name in names(benchmark_data)) {
  sublist <- benchmark_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```


## Benchmark:
```{r}
setwd("/path/to/figures/benchmarks/")

for (name in names(benchmark_data)) {
  sublist <- benchmark_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```


## CC:
```{r}
setwd("/path/to/figures/CC")

for (name in names(CC_data)) {
  sublist <- CC_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```

## CCG10:
```{r}
setwd("/path/to/figures/CCG10/")

for (name in names(CCG10_data)) {
  sublist <- CCG10_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```

## CCR:
```{r}
setwd("/path/to/figures/CCR/")

for (name in names(CCR_data)) {
  sublist <- CCR_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```

## NRCs:
```{r}
setwd("/path/to/figures/NRCs/")

for (name in names(NRC_data)) {
  sublist <- NRC_data[[name]]
  df <- sublist$chain_pair_iptm
  
  # Call the plotting function
  plot_heatmap(df, name)
}
```






# Plot the stats:
## Custom theme:
```{r}
theme_custom <- theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(), axis.text = element_text(size = 11),
  legend.position = "none",
  panel.background = element_blank(),
  plot.background = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  plot.title = element_blank(),
  plot.subtitle = element_blank(),
  plot.caption = element_blank(),
  axis.line = element_line(colour = "black", size = 0.5), 
  panel.grid = element_blank(), 
  legend.background = element_blank(), 
  title = element_blank(), 
  axis.text.x.top = element_blank()
)
```


## Import the data:
```{r}
NRCs_meta <- read.xlsx("/path/to/Data_S1.xlsx", sheet = "3. NRCs")

benchmarks_meta <- read.xlsx("/path/to/Data_S1.xlsx", sheet = "4. cryo-EM Benchmark")

CC_type_meta <- read.xlsx("/path/to/Data_S1.xlsx", sheet = "5. CC-types NLRs")

NRC2_benchmark_meta <- read.xlsx("/path/to/Data_S1.xlsx", sheet = "2. NRC2 benchmark")
NRC2_benchmark_meta$Oligomer <- factor(NRC2_benchmark_meta$Oligomer, levels = c(4:8))
```



### NRCs
```{r}
NRCs_ipTM <- NRCs_meta %>%
  select(Gene, Pentamer.ipTM, Hexamer.ipTM) %>% setNames(c("Gene","pentamer","hexamer"))

NRCs_pTM <- NRCs_meta %>%
  select(Gene, Pentamer.pTM, Hexamer.pTM) %>% setNames(c("Gene","pentamer","hexamer"))

NRCs_chain_pTM <- NRCs_meta %>%
  select(Gene, Pentamer.Chain.pTM, Hexamer.Chain.pTM) %>% setNames(c("Gene","pentamer","hexamer"))


NRCs_ipTM_long <- pivot_longer(NRCs_ipTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "ipTM")

NRCs_pTM_long <- pivot_longer(NRCs_pTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "pTM")

NRCs_chain_pTM_long <- pivot_longer(NRCs_chain_pTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "chain_pTM")



NRCs_ipTM_p <- ggplot(NRCs_ipTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = ipTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

NRCs_ipTM_p

ggsave(filename = "/path/to/figures/NRCs_ipTM.svg", 
       NRCs_ipTM_p, width = 11, height = 2.5, dpi = "retina")



NRCs_pTM_p <- ggplot(NRCs_pTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = pTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

ggsave(filename = "/path/to/figures/NRCs_pTM.svg", 
       NRCs_pTM_p, width = 11, height = 2.5, dpi = "retina")



NRCs_chain_pTM_p <- ggplot(NRCs_chain_pTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = chain_pTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

ggsave(filename = "/path/to/figures/NRCs_chain_pTM.svg", 
       NRCs_chain_pTM_p, width = 11, height = 2.5, dpi = "retina")
```



### CC-types
```{r}
CC_types_ipTM <- CC_type_meta %>%
  select(Gene, Pentamer.ipTM, Hexamer.ipTM) %>% setNames(c("Gene","pentamer","hexamer"))

CC_types_pTM <- CC_type_meta %>%
  select(Gene, Pentamer.pTM, Hexamer.pTM) %>% setNames(c("Gene","pentamer","hexamer"))

CC_types_chain_pTM <- CC_type_meta %>%
  select(Gene, Pentamer.Chain.pTM, Hexamer.Chain.pTM) %>% setNames(c("Gene","pentamer","hexamer"))


CC_types_ipTM_long <- pivot_longer(CC_types_ipTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "ipTM")

CC_types_pTM_long <- pivot_longer(CC_types_pTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "pTM")

CC_types_chain_pTM_long <- pivot_longer(CC_types_chain_pTM, 
                          cols = c(pentamer, hexamer), 
                          names_to = "Type", 
                          values_to = "chain_pTM")



CC_types_ipTM_p <- ggplot(CC_types_ipTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = ipTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

CC_types_ipTM_p

ggsave(filename = "/path/to/figures/CC_types_ipTM.svg", 
       CC_types_ipTM_p, width = 11, height = 2.5, dpi = "retina")



CC_types_pTM_p <- ggplot(CC_types_pTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = pTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

ggsave(filename = "/path/to/figures/CC_types_pTM.svg", 
       CC_types_pTM_p, width = 11, height = 2.5, dpi = "retina")



CC_types_chain_pTM_p <- ggplot(CC_types_chain_pTM_long, aes(x = factor(Gene, levels = unique(Gene)), y = chain_pTM, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pentamer and Hexamer ipTM by Gene", 
       x = "Gene", 
       y = "ipTM") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("pentamer" = "#ef476f", "hexamer" = "#118ab2")) +
  theme_custom

ggsave(filename = "/path/to/figures/CC_types_chain_pTM.svg", 
       CC_types_chain_pTM_p, width = 11, height = 2.5, dpi = "retina")
```




## NRC2 benchmarks:
### Plot the RMSD, ipTM, and pTM:
```{r}
NRC2_hexamers <- NRC2_benchmark_meta %>%
  filter(Oligomer == 6) %>%
  select(Gene, AF3.Model, ipTM, pTM, RMSD)


NRC2_hexamers_iptm_p <- ggplot(NRC2_hexamers, aes(x = factor(AF3.Model, levels = unique(AF3.Model)), y = ipTM, group = Gene)) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = round(ipTM, 3)), vjust = -0.5, hjust = 0.5, size = 3) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  theme_custom

NRC2_hexamers_iptm_p

ggsave(filename = "/path/to/figures/NRC2_hexamers_ipTM.svg", 
       NRC2_hexamers_iptm_p, width = 4, height = 2.5, dpi = "retina")




NRC2_hexamers_ptm_p <- ggplot(NRC2_hexamers, aes(x = factor(AF3.Model, levels = unique(AF3.Model)), y = pTM, group = Gene)) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = round(pTM, 3)), vjust = -0.5, hjust = 0.5, size = 3) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  theme_custom

NRC2_hexamers_ptm_p

ggsave(filename = "/path/to/figures/NRC2_hexamers_pTM.svg", 
       NRC2_hexamers_ptm_p, width = 4, height = 2.5, dpi = "retina")




NRC2_hexamers_RMSD_p <- ggplot(NRC2_hexamers, aes(x = factor(AF3.Model, levels = unique(AF3.Model)), y = RMSD, group = Gene)) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = round(RMSD, 3)), vjust = -0.5, hjust = 0.5, size = 3) +
  scale_y_continuous(limits = c(0, 3), breaks = seq(0, 3, by = 0.5)) +
  theme_custom

NRC2_hexamers_RMSD_p

ggsave(filename = "/path/to/figures/NRC2_hexamers_RMSD.svg", 
       NRC2_hexamers_RMSD_p, width = 4, height = 2.5, dpi = "retina")
```


Plot the stats for different oligomers:
```{r}
NRC2_benchmark_meta_select <- NRC2_benchmark_meta %>% select(Gene, Oligomer,AF3.Model, ipTM, pTM, Min.Chain.pTM)

NRC2_benchmark_meta_select_long <- pivot_longer(NRC2_benchmark_meta_select, 
                                                cols = c(ipTM, pTM, Min.Chain.pTM), 
                                                names_to = "Type", 
                                                values_to = "values")


NRC2_benchmark_meta_select_long$Type <- factor(NRC2_benchmark_meta_select_long$Type, levels = c("ipTM","pTM","Min.Chain.pTM"))


NRC2_benchmark_meta_select_p <- ggplot(NRC2_benchmark_meta_select_long, aes(x = Oligomer, y = values, group = Oligomer, color = Type)) +
  facet_grid(~Type) +
  geom_boxplot() +
  geom_jitter(size = 0.8) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  scale_color_manual(values = c("#F8AC32","#E75831","#49C187")) +
  theme_custom +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 15))

NRC2_benchmark_meta_select_p

ggsave(filename = "/path/to/figures/NRC2_oligomers_stats.svg", 
       NRC2_benchmark_meta_select_p, width = 5, height = 5, dpi = "retina")






# Plot the contacts from cryo-EM and AF3 models:
### Import the contacts from both AF3 and cryo-EM structure
```{r}
# AF3 residues with 4.5 Å distance
contacts_list_AF3 <- read_excel("/path/to/Data_S2.xlsx", sheet = "AF3")

# keep the unique ones
contacts_list_AF3_unique <- table(contacts_list_AF3$contacts) %>% as.data.frame() %>% setNames(c("residue","contacts"))

AF3_contact_residues <- contacts_list_AF3_unique$residue %>% as.data.frame() %>% setNames("contacts")
AF3_contact_residues$contacts <- numeric_values <- as.numeric(levels(AF3_contact_residues$contacts))[AF3_contact_residues$contacts]



# cryo-EM structure contacts
contacts_list_cryo <- read_excel("/path/to/Data_S2.xlsx", sheet = "cryo-EM") %>% as.data.frame()


# merge them into a single dataframe
contacts <- c(1:886) %>% as.data.frame() %>% setNames("position")
  
contacts_df <- contacts %>% 
  left_join(AF3_contact_residues, by = c("position" = "contacts"), keep = TRUE) %>%
  left_join(contacts_list_cryo, by = c("position" = "contacts"), keep = TRUE)

colnames(contacts_df) <- c("position","AF3","cryo-EM")


# prepare for plotting
contacts_df_long <- contacts_df %>%
  pivot_longer(cols = c(AF3, `cryo-EM`),
               names_to = "contact_type",
               values_to = "contact_value")


# Filter out rows where contact_value is NA
contacts_df_long <- contacts_df_long %>%
  mutate(presence = !is.na(contact_value))


# Create the plot
contacts_df_p <- ggplot(contacts_df_long, aes(x = position, y = contact_type)) +
  geom_point(aes(color = contact_type, alpha = presence)) +
  scale_color_manual(values = c("AF3" = "#e63946", "cryo-EM" = "#457b9d")) +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0), guide = "none") +
  scale_x_continuous(breaks = seq(0, 1000, by = 50), limits = c(1, 886)) +
  theme_custom +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 13))

contacts_df_p

ggsave(filename = "/path/to/figures/AF3_vs_cryo_contacts.svg", 
       contacts_df_p, width = 15, height = 3, dpi = "retina")


```